The Kapowski Chronicles: A Complete, Volumetric Cortical Thickness Open Source Pipeline with Evaluation on Public Data

### 2012-06-24 KapowskiChronicles/methods.tex
ENH:  Added template figure.
ENH:  Luis Miguel, Con tus besos.

The first 20 subjects were used to create a population-specific
unbiased average template \cite{avants2010}.  The brain masks corresponding 
to the 20 subjects were warped to the template space using the 
transforms derived during the template building process.  A template 
probability mask was created by averaging the warped brain masks.
For brain extraction of any single individual this ANTS-based LPBA40 template 
is coarsely registered to the single subject brain.  The template
probability brain mask is warped to the individual subject and 
is used as the initial brain mask estimate.  As mentioned previously,
Atropos and binary morphological operations are used to refine the
brain mask estimate.

@@

The nonrigid image registration evaluation project is an ongoing 
framework for evaluating image registration algorithms \citep{christensen2006}.
The initial data set introduced into the project consists of 
16 (8 male and 8 female) high resolution skull-stripped brain 
data with 32 cortical labels manually drawn using published protocol.
Given the gray matter labels, the white matter and CSF were identified 
for each of the 16 subjects using Atropos.  Similar to the LPBA40
data set, a NIREP template was created from 8 subjects and each the
warped labels were used to create probabilistic estimates of the 
labeled region boundaries. These probability maps were used as 
spatial prior probabilities during the 3-tissue segmentation component
of the pipeline.  Using SyN, the NIREP template is registered to the
extracted individual subject brain which is followed by a warping of the 
NIREP priors to the space of the individual subject.  The initial warped 
white matter probability map is used as the weighted confidence mask 
in the follow-up bias correction step.

@@

>>>>

All 40 subjects were used to create a population-specific
unbiased average template \cite{avants2010}.  The brain masks corresponding 
to the 20 subjects were warped to the template space using the 
transforms derived during the template building process.  A template 
probability mask was created by averaging the warped brain masks.
For brain extraction of any single individual this ANTS-based LPBA40 template 
is coarsely registered to the single subject brain.  The template
probability brain mask is warped to the individual subject and 
is used as the initial brain mask estimate.  As mentioned previously,
Atropos and binary morphological operations are used to refine the
brain mask estimate.

@@

The nonrigid image registration evaluation project is an ongoing 
framework for evaluating image registration algorithms \citep{christensen2006}.
The initial data set introduced into the project consists of 
16 (8 male and 8 female) high resolution skull-stripped brain 
data with 32 cortical labels manually drawn using published protocol.
Given the gray matter labels, the white matter and CSF were identified 
for each of the 16 subjects using Atropos.  Similar to the LPBA40
data set, a NIREP template was created from all 16 subjects and each the
warped labels were used to create probabilistic estimates of the 
labeled region boundaries. These probability maps were used as 
spatial prior probabilities during the 3-tissue segmentation component
of the pipeline.  Using SyN, the NIREP template is registered to the
extracted individual subject brain which is followed by a warping of the 
NIREP priors to the space of the individual subject.  The initial warped 
white matter probability map is used as the weighted confidence mask 
in the follow-up bias correction step.

@@

\begin{figure}
  \centering
  \includegraphics[width=90mm]{Figures/template.pdf}
  \caption{Sample multivariate template constructed from a subset of the IXI data (female, age 40--50).  Axial slices of five of the 37 total subjects from this cohort are shown. }
  \label{fig:template}
\end{figure}
